Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-09-12 ms/main.tex
Move figures from my notebook to new notebook
fix some figures

\end{result}

%This result illustrates the crucial role of vertical and oblique transmission: the same cost of cooperation $c$ can lead to remarkably different outcomes if the vertical transmission rate $v$ is below or above the threshold $\hat v$.
% TODO example with figure

@@

%%% Figure: coexistence map - without oblique transmission
\begin{figure}[htb]
\centering
\includegraphics{coexistence_without_oblique.pdf}
\caption{\textbf{Stable and unstable coexistence between cooperation and defection without oblique transmission.}
  The curves show the frequency of the cooperative phenotype $A$ among parents in the next generation $\tilde{p}'$ vs. the current generation $\tilde{p}$ (\autoref{eq:nextgen_parents_vertical_only}).
  The dashed black line is $\tilde{p}'=\tilde{p}$.
  The curves and the dashed line intersect at the polymorphic equilibrium $\tilde{p}^*$ (black circle).
  When the curves are above the dashed line, $\tilde'{p}>\tilde{p}$, then $\tilde{p}$ increase.
  When the curves are below the dashed line, $\tilde'{p}<\tilde{p}$, then $\tilde{p}$ decreases.
  The orange curve, for which the polymorphic equilibrium is stable, is given by $T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, and $\alpha = 0.45$, which give $\gamma_2<c<\gamma_1$ (\autoref{eq:cost_boundaries})
  The blue curve, for which the equilibrium is unstable, is given by $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, and $\alpha = 0.4$, which give $\gamma_1<c<\gamma_2$.
  In both cases there is no oblique transmission, $v=1$; see \autoref{fig:coexistence_with_oblique} for $v<1$.
  }
\label{fig:coexistence_without_oblique}
\end{figure}

%%% Figure: Conditions for fixation

\begin{figure}[htb]
  \centering
  % TODO for some reason figs a and b have a lot of white space on their right side

    \includegraphics[scale=0.75]{boundiries_alpha0.pdf}

    \includegraphics[scale=0.75]{boundiries_non_zero_alpha.pdf}

    \includegraphics[scale=0.75]{boundiries_withAlpha_y_axis.pdf}
    \caption{\textbf{Evolution of cooperation under vertical and horizontal cultural transmission.} 
The figure shows the global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e. unstable coexistence (blue), and stable coexistence of cooperation and defection (yellow).
In all cases the horizontal bias ($T_A-T_B$) is on the x-axis.
(\textbf{a-b})~the cost of cooperation $c$ is on the y-axis; the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries}) are the solid and dashed lines. 
(\textbf{c})~the social association $\alpha$ is on the y-axis; the social association boundaries $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting}) are the solid and dashed lines.
Here, $b=1.3$, $T_A=0.4$. (\textbf{a})~$\alpha = 0$.(\textbf{b})~$\alpha = 0.7$. (\textbf{c})~$c = 0.35$.
  % TODO missing text descriptions of conditions on (3)
  	}
    \label{fig:results2}
\end{figure}

>>>>

\end{result}
These conditions are illustrated in \autoref{fig:result3}.

%This result illustrates the crucial role of vertical and oblique transmission: the same cost of cooperation $c$ can lead to remarkably different outcomes if the vertical transmission rate $v$ is below or above the threshold $\hat v$.

@@

%%% Figure: coexistence map - without oblique transmission
\begin{figure}[htb]
\centering
\includegraphics[scale = 0.75]{coexistence_without_oblique.pdf}
\caption{\textbf{Stable and unstable coexistence between cooperation and defection without oblique transmission.}
  The curves show the frequency of the cooperative phenotype $A$ among parents in the next generation $\tilde{p}'$ vs. the current generation $\tilde{p}$ (\autoref{eq:nextgen_parents_vertical_only}).
  The dashed black line is $\tilde{p}'=\tilde{p}$.
  The curves and the dashed line intersect at the polymorphic equilibrium $\tilde{p}^*$ (black circle).
  When the curves are above the dashed line, $\tilde'{p}>\tilde{p}$, then $\tilde{p}$ increase.
  When the curves are below the dashed line, $\tilde'{p}<\tilde{p}$, then $\tilde{p}$ decreases.
  The orange curve, for which the polymorphic equilibrium is stable, is given by $T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, and $\alpha = 0.45$, which give $\gamma_2<c<\gamma_1$ (\autoref{eq:cost_boundaries})
  The blue curve, for which the equilibrium is unstable, is given by $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, and $\alpha = 0.4$, which give $\gamma_1<c<\gamma_2$.
  In both cases there is no oblique transmission, $v=1$; see \autoref{fig:coexistence_with_oblique} for $v<1$.
  }
\label{fig:coexistence_without_oblique}
\end{figure}

%%% Figure: Boundaries figure - only vertical

\begin{figure}[htb]
  \centering       
    \includegraphics[scale=0.5]{Result2_zero_alpha.pdf}

    \includegraphics[scale=0.5]{Result2__non_zero_alpha.pdf}

    \includegraphics[scale=0.5]{Result2__alpha_on_y_axis.pdf}
    \caption{\textbf{Evolution of cooperation under vertical and horizontal cultural transmission.} 
The figure shows the global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e. unstable coexistence (blue), and stable coexistence of cooperation and defection (yellow).
In all cases the horizontal bias ($T_A-T_B$) is on the x-axis.
(\textbf{a-b})~the cost of cooperation $c$ is on the y-axis; the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries}) are the solid and dashed lines. 
(\textbf{c})~the social association $\alpha$ is on the y-axis; the social association boundaries $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting}) are the solid and dashed lines.
Here, $b=1.3$, $T_A=0.4$. (\textbf{a})~$\alpha = 0$.(\textbf{b})~$\alpha = 0.7$. (\textbf{c})~$c = 0.35$.
  % TODO missing text descriptions of conditions on (3)
  	}
    \label{fig:results2}
\end{figure}

%%% Figure: Boundaries figure - vertical and oblique

\begin{figure}[htb]
  \centering       
    \includegraphics[scale=0.5]{Result3_boundaries.pdf}
    \caption{\textbf{Evolution of cooperation under vertical, oblique and horizontal cultural transmission.} 
The figure shows the global fixation of cooperation (green), global fixation of defection (red) and stable coexistence of cooperation and defection (yellow).
In all cases the horizontal bias ($T_A-T_B$) is negative meaning $T_B>T_A$.
The vertical transmission rate $v$ is on the y-axis; the cost boundaries $\hat\gamma_1$ and $\hat\gamma_2$ (\autoref{eq:cost_boundaries_v}) are the solid and dashed lines. 
Here, $b=2$, $T_A=0.5$, $T_B = 0.7$, $\alpha = 0.7$.}
    \label{fig:result3}
\end{figure}
